Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-14 peakcharacterization_manuscript.Rmd
captions for new figures

@@

>>>>

*caption*: Peak ordering in M/Z compared with ordering in frequency space when a single M/Z to frequency model is used or scan specific M/Z to frequency models are used. For a single peak, the scan level peak M/Z's were extracted, and then frequency values for those M/Z generated using a single common model of M/Z to frequency (*single_order*), or models derived from each scan (*scan_order*). A subset of the peaks end up out of order using scan specific models, implying that a single model should be used across all the scan level data.

@@

*caption*: Histogram of the number of non-zero points across all scans in sliding windows 10 frequency points wide and 1 frequency point apart. The red vertical line denotes the lower 99th percentile of the data, only sliding windows with non-zero counts above the red line will be kept for subsequent use.
